### 2018-06-16 manuscript.tex
Update manuscript.tex

>>>>

\cite{EffeVoge15}:  Each family may have its own threshold of fgc. I think fgc norm has shifted from marraige advantage of social capital of social networking as proposed by Shell-Duncon and her colleagues \cite{ShelWand11}.  To elaborate the shifted values of fgc, what it imply and how to apply the change to policy.
